---
title: "Initial Analysis"
author: "Juliano Palacios-Abrantes"
date: '2019-02-04'
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r setup, eval=T, echo=F, warning=F,message=F, results='hide'}

#### READ ME !!! ####
# Run this chunk before knit so you make sure you have all pkgs installed in R

ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE,repos = "http://cran.us.r-project.org")
  sapply(pkg, require, character.only = TRUE)
}


#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggplot2", #Nice grpahs and spatial analysis
  "cowplot",
  "rgdal",
  "RColorBrewer",
  "knitr",
  "kableExtra",
  "data.table",
  "ggrepel",
  "gridExtra",
  "ggmap",
  "rgeos",
  # "stringr",
  # "stringer",
  "spdep",
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  "purrr",#Spatial analysis 
  # "rgdal", #Spatial analysis 
  "tools", #Spatial analysis 
  "png", # For reading plots in chunk codes
  "grid" # For reading plots in chunk codes
)

ipak(packages)

```


# Methods

These are the methods to follow:

1. Determine which countries have neighboring EEZs  
  1.1. For this we used the Marine regions EEZ maps (We have to change this because it does not discriminate by oceans and we need this) and a routine to identify neighboring polygons,
  1.2. Then we match the DBEM spatial information (e.g. INDEX within EEZ and coordinates) with the neighboring data
2. Overlap distribution maps with neighbors data  
  2.1. For each species we merged the DBEM_Neighbors data with their known distribution (Gab's data)  
3. Determine transboundary if:  
  3.1. Species is present in both neighboring EEZs by INDEX  

Alternatively, we could create a "confidence level" based on a ratio, i.e;
- How many grid cells of both the EEZs is the species present on. A species that covers all cells would have 100% but a species that covers, lets say, all of EEZ1 but only half of EEZ2 would be 75%.  
- Another option is to have the index based on the species distribution. That is to say, what proportion of the total species distribution actually falls within both EEZs....


### Current issues

- How to distinguish between North and South? Example of Brazil, Uruguay and French Guyana

## Data

```{r Speceis_Models, eval = F, echo = T}

# Get the DBEM list of species to extract from other modesl
#GFDL
DBEM_species_G <- data_frame(TaxonKey = list.files("/Volumes/DATA/DATA/DBEM/GFDL26F1"))
#IPSL
DBEM_species_I <- data_frame(TaxonKey = list.files("/Volumes/DATA/DATA/DBEM/IPSL26F1"))
#MPI
DBEM_species_M <- data_frame(TaxonKey = list.files("/Volumes/DATA/DATA/DBEM/MPI26F1"))


# Merge the, and save to send to gabs

DBEM_Species_List <- DBEM_species_I %>% 
  bind_rows(DBEM_species_G,
            DBEM_species_M) %>% 
  group_by(TaxonKey) %>% 
  summarise() %>% 
  filter(str_detect(TaxonKey, "^6"))


# Include species name, as well... 

exploited_species <- read.csv("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv")

DBEM_Species_List <- DBEM_Species_List %>% 
  left_join(exploited_species,
            by ="TaxonKey")


# write.csv(DBEM_Species_List,
#           "DBEM_Species_List.csv",
#           row.names = F)




```



```{r Spatial_Data, eval=T, echo=T, results='hide'}


# Spatial analysis for Countries boundaries from marine regions ####

###_______________________________Read Me_____________________________________________#
#### Data License and references ###
# Marine Regions’ data is licensed under CC-By-NC-SA (https://creativecommons.org/licenses/by-nc-sa/4.0/).
# Flanders Marine Institute (2018). Maritime Boundaries Geodatabase: Maritime Boundaries and Exclusive Economic Zones (200NM), version 10. Available online at http://www.marineregions.org/. https://doi.org/10.14284/312

#### Using the SAU shapefile that contains EEZ per ocean (E.G. Mexico Pacific and Mexico Atlantic)
###________________________________________________________________________________#

# The path
path_world <- "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Spatial_Data/SAU_Shapefile/"
#The File
fnam_world <- "SAUEEZ_July2015.shp"
#Load it!

# World_EEZ <- readOGR(dsn = path_world,
                     # layer =file_path_sans_ext(fnam_world))


World_EEZs <- st_read(dsn = path_world,
                      layer = file_path_sans_ext(fnam_world))

# head(World_EEZs)

#### Grid cell information ####

# List of DBEM INDEX within the EEZ
#Data provided by Vicki Lam

EEZIDs_List <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/Updated_EEZList_17June2016.xlsx")
EEZ_CellID <- read_excel("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/EEZ_CellID.xlsx")

colnames(EEZ_CellID) <- c("EEZID","INDEX")

# DBEM Coordinate system
Coor <- fread("~/Documents/UBC/Oceans_Project/Distribution/DBEM/Data/Lon_Lat_DBEM.txt",header = FALSE)
colnames(Coor) <- c("INDEX","Longitude","Latitude")

# Species list

# DBEM exploited species list 
# exploited_species_list <- fread("/Volumes/DATA/PROJECTION exploited species ENM/exploited_species_list.csv")

# Use thisone for testing 
Selected_Species <- fread("~/Documents/UBC/Oceans_Project/Distribution/By Cell/Cell_Data/List_Species.csv") %>% 
  select(1:2)


```


### Determine which countries are neighbors

```{r Testing_Neighbors, eval=F, echo=T}
# Determine which countries are neighbors

# Method adopted from Adrew Heiss
# https://gist.github.com/andrewheiss/926b9d60a26e29f6bf32

# Subset data for testing
South_America <-c("Mexico","Argentina","Chile","Peru","Ecuador","Colombia","Venezuela","Brazil")

South_Americasp <- World_EEZ[World_EEZ@data$Name %in% South_America, ]

#Look for comments in previous chunk

# Get the list using the poly2nb function
Neighbor_List <- poly2nb(South_Americasp)

# Convert te nb data to a Matrix of crossing references
Neighbor_Matrix <- nb2mat(Neighbor_List,
                          style="B", 
                          zero.policy=TRUE)

# Rename the matrix axis
colnames(Neighbor_Matrix) <- rownames(Neighbor_Matrix)


# Get the names of the countries for identifying them
Country_Names <- data_frame(id = row.names(South_Americasp@data),
                            Country_Territory = as.character(South_Americasp@data$Territory1),
                            Neighbor_Territory = Country_Territory)

# Clean up and transform the neighbor matrix
SA_Neighbors <- as.data.frame(Neighbor_Matrix) %>%
  mutate(country = row.names(.)) %>%  # Convert row names to actual column
  gather(neighbor, present, -country) %>%  # Convert to long
  filter(present == 1) %>%  # Only look at cells with a match
  # Add country names
  left_join(select(Country_Names,
                   -Neighbor_Territory), by=c("country" = "id")) %>%
  left_join(select(Country_Names, 
                   -Country_Territory), by=c("neighbor" = "id")) %>% 
  select(4,5) # select final column

head(SA_Neighbors)

# Remove duplicates (e.g. Country A - Country B and Country B - Country A)
### NOTE, I'm going to use the already created one. Load it fiz it and save it with the same name.

SA_Neighbors_Clear <- SA_Neighbors[!duplicated(SA_Neighbors[1:length(SA_Neighbors)]), ] 


#### Works beautifully! 
```


```{r Determine_neighbors_Test, eval = F, echo=T}

#### SF package 

SAU_Regions <- as.data.frame(unique(World_EEZs$Name))

Test_Countries <-c("Mexico (Atlantic)","Mexico (Pacific)","Guatemala (Caribbean)","Guatemala (Pacific)","Belize")

# Test_sp <- World_EEZ[World_EEZ@data$Name %in% Test_Countries, ]

Test_sf <- filter(World_EEZs, Name %in% Test_Countries)

# ggplot(Test_sf) +
#   geom_sf() # 5 min 

# Adds to the shapefile a column with the neighbourds 
Neighbours_sf <- Test_sf %>%
  mutate(Neighbours = map(.x = geometry, 
                          .f = st_intersects, 
                          y = st_geometry(Test_sf))
         ) %>% 
  st_transform(3832) %>% 
  st_simplify(10000)

head(Neighbours_sf)

```

### Merge Neighbors with DBEM data

```{r Data_Wrangling, eval=T, echo=T, results='hide'}

### Match DBEM list of countries wth Neighbors
Matching_Names <- Neighbours_sf %>% 
  semi_join(EEZIDs_List,
            by ="EEZID") # Only half of them match

head(Matching_Names)

```



```{r Trans_Spp_Function, eval=T,echo=T,warning=F,message=F}

# Function to determine whether or not a species is transboundary

# Varibales needed
# Spp: Species to be abalized, data with presence/absence per gridcell
# Index_EEZ: Reference list of all INDEX that fall within EEZs
# Neighbors: Reference list of all the neighboring EEZs that each country has

# The function
Trans_Spp_Fun <- function(Spp,Index_EEZ,Neighbors){
  
  Trans_Spp <- Spp %>%
    filter(V1 >= 1) %>% # Filter only presence
    left_join(Index_EEZ,
              by = "INDEX") %>% # Match the species distribution to the Countries EEZs
    group_by(Country_Territory=Name,
             Neighbor_Territory) %>% 
    summarise(N_INDEX = n()) %>% # The number of cells present within each country's EEZ
    mutate(Trans = 1) # Include one transboundary species
  
  
  # Result 1. Number of Countries that share the species
  Trans_Spp <- Neighbors %>% 
    left_join(Trans_Spp,
              by = c("Country_Territory","Neighbor_Territory")) %>% 
    mutate_if(is.numeric, funs(replace(., is.na(.),0))) #%>% # Replaces NAs for 0's to sum
    # mutate(Species = ifelse(Trans > 0,paste(Spp[1,2]),NA)) # Includes the species in question
  
  # Result 2. List of Countries that share the Species ####
  
  Countries_with_Specie <- Trans_Spp %>% 
    filter(Trans == 1) %>% 
    group_by(Neighbor_Territory) %>% 
    summarise()
  
# Function Results  
  
  # print(Countries_with_Specie) # Prints the countries that share such species
  return(Trans_Spp) # A dataframe with each country and neighbouring states sharing the species
} # End function


### Testing Function ####
# WORKS!!!!

# Load Species data
# D_Path <- paste("./Data/123",".csv",sep="")

# Reads file
# Species <- read.csv(D_Path)

# Call the function (Works)
# Function_Test <- Trans_Spp_Fun(Species,DBEM_Neighbors_Data,Neighbors);View(Function_Test)

```

```{r World_Trans_Spp, eval=T,echo=T,warning=F,message=F}

World_Trans_Spp <- function(Species_List,Data_Path,Result){
  
  # Repeat for each species
  for (s in 1:nrow(Species_List)){ # Original code
    
    # Load species distribution data
    Species_Distribution_Path <- paste(Data_Path,Species_List[s,2],".csv",sep="")
    
    # Reads file
    Species_Distribution_Data <- read.csv(Species_Distribution_Path)
    
    # Pastes species name
    Species_Name = Species_List[s,1]
    
    # Call function to determine transboundary species
    Partial <- Trans_Spp_Fun(Species_Distribution_Data,
                             DBEM_Neighbors_Data,
                             Neighbors) %>% 
      mutate(Species = ifelse(Trans > 0,paste(Species_Name),NA)) # Include species name
    
    ### Result 1. Numnber of transboundary species by Country ####
    if(s == 1){
      Trans_Country = Partial
    }else{
      Trans_Country[,3] <- Trans_Country[,3] + Partial [,3] # Sum transboundary species
      Trans_Country[,4] <- Trans_Country[,4] + Partial [,4] # Sum Indexes within eez with TS
      Trans_Country[,5] <- ifelse(Trans_Country[,4] >= 0, paste(Trans_Country[,5],Partial[,5], sep=";"),Trans_Country[,5]) # Paste the species that are transboundary
    }
    
    # Result 2. Number of Countries per Transboundary Species ####
    
    Countries_with_Specie <- Partial %>% 
      filter(Trans == 1) %>% 
      group_by(Neighbor_Territory) %>% 
      summarise() %>% 
      summarise(Number_EEZ = n(),
                Countries = paste(Neighbor_Territory,
                                  collapse = ";")
      ) %>% # Number of territories in this species
      mutate(Species = Species_Name)
    
    
    if(s == 1){
      All_Countries_with_Specie <- Countries_with_Specie
    }else{
      All_Countries_with_Specie <- All_Countries_with_Specie %>% 
        bind_rows(Countries_with_Specie)
    }
    
  }# Closes species list
  
  # Function return
  if(Result =="Country"){ # returns results based on countries 
    return(Trans_Country)
  }
  if(Result == "Species"){ # returns results based on species 
    return(All_Countries_with_Specie)
  }
}

### Testing Function ####
# (Works!!!!!!!!)

### Dummy data ###
# SppA <- Julianus_Coor %>% 
#   filter(V1 >= 100000)
# 
# SppB <- Julianus_Coor %>% 
#   filter(V1 <= 100000)

# write.csv(SppB,
#           "456.csv",
#           row.names = F)

Dummy_Species <- data.frame(
  Species = c("SpeciesA","SpeciesB"),
  TaxonKey = c(123,456)
  )

D_Path <- "./Data/"

Function_Test <- World_Trans_Spp(Dummy_Species,D_Path, Result = "Country")

```

```{r Final_Analysis, eval=T, echo=F}

# Varibales needed
# Species_List
# Data_Path

# Data_Path <- Drobo... Gabs... Distributions...
# DBEM_Species <- Selected_Species
  
  
# World_Trans_Spp(DBEM_Species,Data_Path)


```