---
title: "Title: Fish do not need Visas: the transboundary nature of world fished species (70/96 character maximum)"
authors: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, William W.L. Cheung^1^"
date: "Affiliations: ^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada, ^2^ Yale"
# subtitle: "Fish do not need Visas (16/40 character maximum)"
output:
  pdf_document:
    fig_caption: yes
  word_document:
    reference_docx: ./Manuscript_Instructions/science_template.docx
geometry: margin=1in
editor_options:
  chunk_output_type: console
bibliography: ./References/FishForVisa_Ref.bib
csl: ./References/science.csl
---

```{r Ch2_setup, eval = T, echo=F, warning=F,message=F, results='hide'}

#### READ ME !!! ####
# Run this chunk before knit so you make sure you have all pkgs installed in R

ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE,repos = "http://cran.us.r-project.org")
  sapply(pkg, require, character.only = TRUE)
}


#### Library ####
packages <- c(
  "dplyr", # Data manipulation
  "knitr",
  "kableExtra",
  "png",
  "grid",
  "here"
  
)

ipak(packages)

```

<!-- # Instructions for submission -->

<!-- - Journal: *Science*  -->
<!-- - Information to authors (https://www.sciencemag.org/authors/science-information-authors) -->
<!-- - There are two types of article: -->

<!-- -- **Reports** (up to ~2500 words including references, notes and captions–corresponds to ~3 printed pages in the journal) present important new research results of broad significance. Reports should include an abstract, an introductory paragraph, up to four figures or tables, and about 30 references.  -->

<!-- Policy Forums (1000 to 2000 words, 1-2 figures, and up to 15 references) presents issues related to the intersections between science and society that have policy implications. -->


<!-- In both cases Materials and Methods should be included in supplementary material -->

<!-- --- Instructions for preparing an initial manuscript https://www.sciencemag.org/authors/instructions-preparing-initial-manuscript -->


<!-- - Reviewers: Names, affiliations, and e-mail addresses of up to five potential reviewers and up to five excluded reviewers. -->

# **One Sentence Summary** (~ 125 characters)

<!-- A brief teaser statement highlighting main result of the paper, understandable by a scientist not in your field, without jargon or abbreviations. This will appear online adjacent to the title and should not repeat phrases already present there -->


- Field code: *Fisheries*

# **Abstract** (~125 words)

<!-- An opening sentence that sets the question that you address and is comprehensible to the general reader, background content specific to this study, results, and a concluding sentence. It should be a single paragraph. -->


<!-- # Introduction (~600 words) -->

Species are not randomly distributed in the world. The area in space and time where a stable population lives and reproduces is determined by the species' fitness response to a series of biotic and abiotic factors [@Hunch] and their influence in the evolutionary process [@REF]. Species distributions are key elements in marine resources management as human-made spatial boundaries are a major part of the management system [@Song:2017iua]. However, incorporating the concept of species distribution has not allays been the case in fisheries management, nor policy [@Alexa]. The delimitation of Economic Exclusive Zones (EEZs) in the arly 80's virtually splitted the distribution of many species, creating shared species between nations, and adding another level of complexity to fisheries management. However, 40 years after their establishment, the question of how many shared species exists in the world based on their distribution is still unanswered. In here, we take the most detailed database of marine fished species to show that many species are shared, representing an important contribution to national economies and food security, and highlighting the importance to acknowledge this in the policy arena.

From 1973 to 1982 the members of the United Nations held a series of meetings to discuss regulations regarding the high seas, a region of international common property, which, at that time, represented waters after 12 miles from shore [@McRae and Munro, 1989]. The establishment of the UN Convention on the Law of the Sea (UNCLOS) allowed coastal states to claim jurisdiction over 200 nautical miles of their coasts [@UN:1982]. Despite intended to improve fisheries management by granting property rights over shared resources, this arbitrary delimitation of management area had no input from biogeography; ignoring species distributions created what we know today as shared stocks [@REF]. The Food and Agricultural Organization (FAO) recognizes three types of shared stocks: (*i*) transboundary, those stocks that are shared by 2 or more neighboring coastal nations; (*ii*) straddling, those stocks that are shared by two or more nations and also the high seas; and (*iii*) highly migratory stocks; species that are found in the EEZs of coastal nations that are not necessarily neighbors, and the high seas. 

The origination of shared stocks required the establishment of new fisheries management methods. Managers and scientists adopted a game theory approach where collaboration would most likely result in the best overall outcome for nations sharing a common resource [@REF]. Lack of collaboration in shared stocks threatens the stock's sustainability [@REF], reduces the profitability potential of the fishery [@REF], and creates conflict between coastal nations [@REF-Jessica?]. Moreover, new emerging conflicts are expected as climate change shifts the distribution of marine species and new shared fisheries emerge [@Pinsky:2018cb]. 

There is a gap in assessing transboundary species in the world based on their spatial distribution. It was estimated in 1997 that there could be up to 1,500 transboundary fish species in the world, however, such estimation lacked a proper assessment due to limited information at the time [@Caddy:1997ue]. More recently, it was estimated there were 344 shared species, representing a capture of 34.2 × 10^6^ t and a global landed value of USD 30.7 × 10^9^ [@Teh:2015gd]. While this represents a good baseline to start, the analysis was based on a literature review of shared species and did not include a mechanistic way of determine the transboundary nature of the species [@Teh:2015gd]. Therefore, 40 years after UNCLOS, the question of how many transboundary species exists in the world is still unanswered. This is of uppermost need as the fisheries management approach differs substantially between EEZ-discreet and shared species [@Mills]. 

 <!-- **Results and discussion** (1000 words) -->

We combined a series of datasets and species distribution models to estimate the number of transboundary fished species and their contribution to food security and economics of the world. We adopted the UN definition of transboundary stocks (shared by neighboring EEZs) but carried the analysis at the species level, rather than stocks (populations within a species), due to lack of stock-specific spatial and ecological information on all of the fished species. Our results suggest that there are XXX transboundary species in the world that account for XXX t landings generating USD xxx in fishing revenue to a total of USD xxxx in the fishing sector. These numbers represent an important contribution to global fish production and revenue estimated in XXX and XXX, respectively, highlighting the importance of transboundary stocks worldwide[@REf][@REf].

Regional variation show higher frequency of transboundary species within EEZs along the South China sea, western central Atlantic, and the Mediterranean sea, followed by the Eastern north Atlantic (Fig 1). The overall fish production of transboundary species is relative lower than the number of species within each EEZ, with the exception of some punctual cases like Peru, Chile, Norway, and Ireland where fewer species produce higher landings (Fig 1).

```{r Call_Map, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by EEZ and their production by country"}

img <- readPNG(here("./Figures/Fig1.png"))
grid.raster(img)
```

It is not surprising then, that countries within this regions hold the most amount of transboundary species. Some African, Asian, and European countries house over 100 species within their EEZs. Only the US presents over 100 transboundary species outside those continents, once all three sub-EEZs (Atlantic and Pacific coast as well as Alaska arctic and subarctic) are accounted for (Fig. 2).


```{r Call_Country_Circular, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary and discrete species by country and continent"}

img <- readPNG(here("./Figures/Fig2.png"))
grid.raster(img)
```


<!-- Will run statistics to see if I can show the "why" of trans spp -->
There is no clear visual pattern regarding transboundary and discrete species, however, from the three countries that house the most amount of discrete stocks, Australia, New Zeland and the US are among the larger in terms of EEZ length, in the other hand, Brazil has only two neighbors along its large latitudinal coast, suggesting not a lot of connection points for sharing species.
<!-- End of statistics paragraph -->

All species that share over >100 countries are widely distributed pelagic species such as Wahoo (*Acanthocybium solandri*), Common thresher shark (*Alopias vulpinus*), and tunas (*Thunnus sp.*) with a median of 65, 42, and 38 species per pelagic oceanic, bathymetric and nerictic species, respectively. The median for all other ecosystem preferences is under 35 as many of these species are not so widely distribute globally.

```{r Call_Spp_Circular, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of countries shared by transboundary species. Showing only species that share > 20 countries"}

img <- readPNG(here("./Figures/Fig3.png"))
grid.raster(img)
```





<!-- # **References** (up to 40 for reports and 15 for policy forum) -->

<!-- # **Acknowledgments* * -->

<!-- ## Funding: include complete funding information;  -->
<!-- ## Authors contributions: a complete list of contributions to the paper (we encourage you to follow the CRediT model), -->
<!-- ## Competing interests: competing interests of any of the authors must be listed (all authors must also fill out the Conflict of Interest form). Where authors have no competing interests, this should also be declared. -->
<!-- ## Data and materials availability: Any restrictions on materials such as MTAs.  -->


# Materials and Methods

In here we present a novel method to estimate whether or not a species is transboundary. Our method is based on a series of criteria to be met and the overlap of species distributions and the spatial boundary of the world's EEZs. For the current analysis we work at the species level and adopt FAO's definition of transboundary species as those that occur within the Exclusive Economic Zone (EEZ) of two or more neighboring countries [@Munro:2002uf; @FAO]. All data was scaled at a 0.5 degree latitude x 0.5 degree longitude grid cells (*n* = ~180,000 grid cells).

## Databases on species geographic distributions

To determine the pool of transboundary marine species exploited by fisheries within each of the world's EEZs we first extract all the commercial marine fish or invertebrate species from the *Sea Around Us* database (http://www.seaaroundus.org and determined their current distributions. For this, we used four species-distributions data sources based on (*i*) observational data, (*ii*) an Environmental Niche Model (ENMs), (*iii*) a life-history-based distribution model, and (*iv*) fisheries catch data (**Table x**). Each source represent a different method of estimating the distribution of a given species and thus, provides a more robust result. Only those commercial fished species that had data from all four sources were included in the analysis, and therefore the final dataset comprised XXX species, XX% of the reported marine species in the SAU database and XX% of the reported taxa of the FAO (**See S1_Data**).

*i* The occurrence data was collected from five publicly available repositories; Fishbase (http://fishbase.org), the Global Biodiversity Information Facility (GBIF; https://www.gbif.org/), the Ocean Biogeographic Information System (OBIS; https://obis.org/),  the Intergovernmental Oceanographic Comission (IOC; http://ioc-unesco.org), and the International Union for Conservation of Nature (IUCN; https://www.iucn.org/technical-documents/spatial-data) [@Reygondeau:2019uh].  

In addition to the occurrence data we use two different methods to estimate species distributions, hereafter referred as ENM-Nereus and SDM-SAU. Although they use the same data, the models are structurally different complementing each other and providing robustness to the results.

*ii* The ENM-Nereus consists in a multimodel approach based on a Bioclim and a Bososted Regression Tree model [@Thuiller:2009gp], a Maxtent model [@Phillips:2006ff], and a Non-Parametric Probabilistic Ecological Niche Model [@Beaugrand:2011fd]. Environmental variables modeled were sea surface temperature, surface pH, surface oxygen concentration, and vertically integrated (0–100 m) net primary production (NPP) [@Asch:2018ca]. The ENM-Nereus employed all of the observational data-sources previously mention. Global environmental conditions were obtained and results averaged from three Earth System Models developed by the Geophysical Fluid Dynamics Laboratory's (GFDL- https://www.gfdl.noaa.gov/earth-system-model/), the Institute Pierre Simon Laplace (IPSL- www.icmc.ipsl.fr/), and the Max Planck Institute for Meteorology (MPI- www.mpimet.mpg.de/en/science/models/). For each species, we only considered models with an area under the curve larger than 0.7 and outputs from the models were average between *1970* and *2000* [@Asch:2018ca; @Reygondeau:2019uh].

*iii* The SDM-SAU model follows a five-steps process based on species-specific life history information, rather than environmental variables [@Close:2006ux; @Palomares:wg]. For each commercial fish species, the model first uses the FAO major fishing areas and countries EEZs to determine a broad distribution. It then uses life history information to delimit its range within the FAO fishing area (e.g. thermal preference, depth limits). The range is delimited even further by expert-review polygons and compared with that of AquaMaps [@Kaschner:2016tl], OBIS and GBIF occurrence data. The model then determines a species habitat preference based on the assumptions that the relative abundance of a species is determine by the number of habitats in a grid cell and the distance of the species to each habitat, and the importance of the habitat to the species size. Finally, the species equatorial submergence (e.g. the latitudinal region where a species is not seen in between poles) is estimated for each species.

*iv* The previous models combine observational data with a series of biotic and abiotic information to determine the probability of a species to be in a given space and time. However, this does not mean that the species in question will actually be there. Although the models used have their own methods of double-check species distributions (e.g. ENM-Nereus uses four different species distribution algorithms and SPD-SAU verifies with other models), we used  a fourth data-source to corroborate the models' outputs. The *Sea Around Us* estimates catch that was not originally reported in the FAO database for each country based on all publicly available information sources. Fishing catch are also spatially allocated following a country-by-country catch reconstruction and spatial layers according to each species [@Zeller2016]. Thus, we used the SAU catch reconstruction from 1970 to 2000 as the fourth dataset to estimate transboundary species and was also used to estimate their catch contribution within EEZs (average 1970-2000).

```{r Data_Table, eval = T, echo = F}

Dasets_names <- c(
  "Occurrence",
  "ENM-Nereus",
  "SDM-SAU",
  "Catch-SAU"
)
Brieff_Description <- c(
  "Occurrence data from multiple sources",
  "Environmental niche model based on environmental variables and different algorithms",
  "Species distribution model based on species traits",
  "Spatial catch allocation based on country-by-country reconstructions"
)

Sources <-  c(
  "Reygondeau 2019",
  "Asch et al., 2017 & Reygondeau 2019",
  "Palomares et al., 2016",
  "Zeller et al., 2016"
)

data.frame(Dasets_names,
           Brieff_Description,
           Sources) %>% 
  kable("latex", booktabs = T,
        caption = "Summary table of data sources ussed in the current analysis") %>%
  kable_styling(full_width = F) %>%
  column_spec(2,width = "8cm") %>% #wraps text in column2
  column_spec(3,width = "3cm") #%>% #wraps text in column2

```

## Determine if a species is transboundary

We developed a four-criteria method for determining whether or not a species was transboundary. Only species that meet all criteria were considered as transboundary species and the analysis was done only within the EEZs of coastal states. In some cases, criteria also work as indexes to measure the uncertainty in the analysis. All of the analysis was done in the statistical software *R version 3.5.2 (2018-12-20)* and code is available at https://github.com/jepa/FishForVisa.

### Criteria 1; Neighbouring EEZs

As previously mentioned, we define transboundary species as those marine species that happen within the EEZs of two or more neighboring countries. Hence, the first criteria was that the species would only be transboundary between two neighboring countries, regardless of the species extended distribution. This way, a species such as Atlantic cod (*Gadus morhua*) distributed along the north Atlantic, was only considered transboundary between each of the neighboring nations covering its distribution, rather than the region as a whole. We assume that this would reduce the differences between species and stock as is more likely that neighboring species belong to the same stock, rather than, lets say, Cod in Norway and Canada. However, the analysis here presented was kept at the species level. 

We define the EEZ boundaries using the SAU shapefile (updated 1 July 2015, available from http://www.seaaroundus.org) that sub-divides EEZs by regions (e.g. Mexico Pacific and Mexico Atlantic) and determine the intersections between polygons using the *sf* *R* package [@SF:package]. When estimating transboundary species, we filter out those shared by the EEZs sub-regions, and when aggregating by country we only counted the species once, if it appears in more than one sub-region. Species that were present in EEZs that were non-continental territories neighboring other countries were kept (e.g. Argentina and Falkland Islands), but removed when the non-continental territory belonged to the same nation (e.g. Brazil and Fernando de Noronha).

### Criteria 2; Data agreement

We use the occurrence database, the ENM-Nereus model, and SDM-SAU model to determine the presence of each species within each of the 0.5 x 0.5 grid cells. We computed a *Species Index* by dividing the number of datasets that confirm presence of a species in a grid cell over the total amount of datasets (*n* = 3). The index is unit-less and represents a scale from 0.3 to 1 where 0.3 means only one dataset reports presence of the species in a grid cell and 1 means agreement between all datasets. We selected only those cases where *Species Index* = 1 to get a more conservative estimate of transboundary species (**S1_Map_per_dataset**). 

### Criteria 3; Modeling verification

We assume that a species was only present in a given grid-cell if it was reported in the SAU catch database. Therefore, all species that were not reported as caught in any single year between the reference years (1970 to 2000) in a given grid-cell were dropped, regardless of the *Species Index*. The assumption relies in that if a commercial species is projected within any fishing country, such species would have been fished, and thus reported at some period of time, and thus validating the models.

### Criteria 4; Spatial distribution

Finally, in order to have a more robust result and do not determine a transboundary species based on the presence in a single 0.5 x 0.5 grid cell within an EEZ, we computed an *Area Index*. The *Area Index* consist in the proportion of the total species distribution within both EEZs that each neighboring EEZ has. We determine that a species would be transboundary if both neighboring EEZs enclosed over 25% of the species joint distribution. Such threshold can be lowered for a more relaxed result or increased for a more conservative estimate (**S2_Hist_per_Treshold**).

## Fisheries trends

Fisheries are important contributors to the world economy and livelihoods. We estimated the economic contribution of transboundary species for each country using global ex-vessel price [@Tai2017]. The data includes ex-vessel price from multiple sources and a structured interpolation method (e.g. similar countries, species) to fill in data gaps [@Sumaila:2015uc]. Additionally, we used a previously estimated country-level multiplyer to understand the total direct, indirect, and induced impact of transboundary species on each country [@Dyck:2010ez]. A continent average was used when no country-level multiplyer was available.

We use the SAU catch data to estimate catch trends over time and determine the potential exploitation status of each species within a EEZ [@Grainger:1996tk; @Kleisner:2011wn]. Despite a possible overestimation of overexploited and collapsed stocks when using only catch data [@Branch:2011br], this method can still shed a light on stock status when only catch data is available [@FAO:2011vz; @FAO:2018KK; @Kleisner:2011wn]. However, the results should be seen as potential species status, rather than the true status of each species. We only assessed species within each EEZ that had at least ten years of data between the first and last reported landings with at least five consecutive data years, and their catch was more than 1,000 tonnes. Five categories were drown from the method depending on the year's catch, the maximum catch over time and the minimum catch after the catch peak (**Table XX**). Finally, we reported the predominant status over the last ten years of catch data (2004-2014).


```{r Status_Table, eval = T, echo = F}

Stock_Status <- c("Rebuilding","Developing","Max Exploited","Over Exploited","Collapsed","No Status")

Rules <- c(
  "(Year of Catch > Year Post Max. Min. & Post Max Min Catch < (Max Catch*0.10)) & (Catch > (Max Catch*0.10) & Catch < (Max Catch*0.50))", # Reb.
  "Year of Catch < Year of Max. Catch & Catch <= (Max Catch*0.50) or Year of Max Catch = Last Year of data)", #Dev.
  "Catch > (Max Catch*0.50)", #Max Exp.
  "Year of Catch > Year of Max. Catch & (Catch > (Max. Catch*0.10) & Catch < (Max. Catch*0.50)", # Over.
  "Year or Catch > Year of Max. Catch & Catch < Max. Catch*0.10", # Colla.
  "Non of the above rules applyed"
)


data.frame(Stock_Status,
           Rules) %>% 
  kable("latex", booktabs = T,
        caption = "Rules to determine the status of each transboundary species") %>%
  kable_styling(full_width = F) %>%
  column_spec(1,width = "3cm") %>% #wraps text in column2
  column_spec(2,width = "13cm") #%>% #wraps text in column2

```


```